---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bis620.2023

<!-- badges: start -->
[![R-CMD-check](https://github.com/zxzalisa/bis620.2023/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/zxzalisa/bis620.2023/actions/workflows/R-CMD-check.yaml)
[![test-coverage](https://github.com/zxzalisa/bis620.2023/actions/workflows/test-coverage.yaml/badge.svg)](https://github.com/zxzalisa/bis620.2023/actions/workflows/test-coverage.yaml)

<!-- badges: end -->

The bis620.2023 package serves as a unified platform designed for interactive data exploration and analysis. It caters to data analysts, researchers, and students, offering a user-friendly interface for dataset exploration and visualization without the need for extensive coding, thanks to the Shiny App integration. This interactive tool can generate histograms for phases, conditions, and designs, as well as dynamic word clouds based on query words or numbers, all customizable within the page panel.

## Links 

- [Coverage tests](https://github.com/zxzalisa/bis620.2023/actions/workflows/test-coverage.yaml)


## Installation

You can install the development version of bis620.2023 from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("zxzalisa/bis620.2023")
```

## Example

Here are several snapshots of the shiny app which demonstrates the added functions.

```{r example}
library(bis620.2023)
launchmyapp()
```

